How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-19?

### 2024-04-09 Main Paper/paper.qmd
fianl edit

---
title: "How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-19?"
author: 
  - Raghav Kanda
thanks: "Code and data are available at: "
date: April 10, 2024
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: refer.bib
---

>>>>

---
title: "How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-19?"
author: 
  - Raghav Kanda
thanks: "Code and data are available at: https://github.com/o8RaV/How-does-the-frequency-and-duration-of-social-media-usage-correlate-with-indicators-of-mental-health"
date: April 10, 2024
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: refer.bib
footer: "Code and data are available at: https://github.com/o8RaV/How-does-the-frequency-and-duration-of-social-media-usage-correlate-with-indicators-of-mental-health"
---
